Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-03-13 scagnostics.Rmd
Added first version of measure definitions

*** Motivating example ??

@@

* Outlying: Outliers are defined in non-parametric fashion via the edge length in the MST, where the 25% and 75% quantil edge length define a threshold value $w=q_{75}+1.5(q_{75}-q_{25})$ above which an edge is considered long. The outlying measure is then calculated as $c_{outlying} = \frac{\mathrm{Total\ length\ of\ long\ edges}}{\mathrm{Total\ length\ of\ all\ edges}}$. Note that outlying points are not considered in the calculation of the other measures.
* Skewed: Skewness is defined via the distribution of edge length in the MST, $q_{skew}=\frac{q_{90}-q{50}}{q_{90}-q_{10}}$. This is inverted as $c_{skew}= 1-w(1-q_{skew})$ to account for binning effects that result in decreasing values of $q_{skew}$ with increasing n.
* Sparse:

>>>>

*** Motivating example ??
This could be the pdf fit data, more structure and shape than other datasets we have?

@@

* Outlying: Outliers are defined in non-parametric fashion via the edge length in the MST, where the 25% and 75% quantil edge length define a threshold value $w=q_{75}+1.5(q_{75}-q_{25})$ above which an edge is considered long. The outlying measure is then calculated as $c_{outlying} = \frac{\mathrm{Total\ length\ of\ long\ edges}}{\mathrm{Total\ length\ of\ all\ edges}}$. Note that outlying points are not considered in the calculation of the other measures.
* Skewed: Skewness is defined via the distribution of edge length in the MST, $q_{skew}=\frac{q_{90}-q{50}}{q_{90}-q_{10}}$. This is inverted as $c_{skew}= 1-w(1-q_{skew})$ to account for binning effects that result in decreasing values of $q_{skew}$ with increasing n.
* Sparse: A second measure based on the distribution of edge lenths, we define $c_{sparse} = w q_{90}$. It takes large values if points are concentrated in well separated parts of the plane, and low values if they are distributed approximately on a lattice.
* Clumpy: To indicate the clustering of points the Clumpy measure is defined as $c_{clumpy}=\max\limits_{j}[1-\max\limits_{k}[\frac{length(e_k)}{length(e_j)}]]$ where we maximise the edge length $length(e_k)$ in the smaller of two subgraphs generated by removing a single edge $e_j$ from the MST. Note that $c_{clumpy}$ will take large values (close to one) if a long edge is separating clustered points connected by short edges.
* Striated: We define an edge as striated if they have a large angle with one of the neighboring edges, concretely $cos(angle) < -0.75$, and the corresponding measure $c_{striate} = \frac{Number of striated edges}{Number of all edges}$. FIXME is this really correct?
* Convex: The convex measure is defined as $c_{convex}= w\frac{area(A)}{area(H)}$ where $A$ is the alpha hull and $H$ the convex hull.
* Skinny: The skinnyness of a polygon can be measured as the ratio of the perimiter to the area. We define $c_{skinny} = 1 -  \frac{\sqrt{4\pi area(A)}}{perimeter(A)}$, where the normalisation is chosen such that $c_{skinny} = 0$ for a circle, and values close to one for skinny polygons.
* Stringy: need to check, should be $c_{stringy} = \frac{diameter(MST)}{lenght(MST)}$ where diameter is longest connected path, and lenght the total lenght (sum of all edgest), i.e. we are measuring branch structure, no branches means $c_{stringy}=1$.
